---
title: "**DATA TIDYING PRESENTATION**"
author: "*Amalia Jiménez Toledano*"
output: 
  revealjs::revealjs_presentation:
    theme: sky
    center: T
    self_contained: false
    highlight: kate
    transition: concave
    css: custom.css
    reveal_options:
      slideNumber: true
---


```{r include=FALSE}
library(Stat2Data)
library(ggplot2)
data(Clothing)
summary(Clothing)
library(knitr)
library(plotly)
library(tidyverse)
```

# READ THE DATA AND SUMMARY

**The variables of the data are the following:**

<p class="fragment" data-fragment-index="6">.**ID**: 	Case ID</p>
<p class="fragment" data-fragment-index="6">.- **Amount**: Net dollar amount spent by customers in their latest purchase from this retailer</p>

- **ID**: 	Case ID
- **Amount**: Net dollar amount spent by customers in their latest purchase from this retailer
- **Recency**:	Number of months since the last purchase
- **Freq12**:	Number of purchases in the last 12 months
- **Dollar12**:	Dollar amount of purchases in the last 12 months
- **Freq24**:	Number of purchases in the last 24 month
- **Dollar24**:	Dollar amount of purchases in the last 24 months
- **Card**:	1 for customers who have a private-label credit card with the retailer, 0 if not

## DATABASE CONSIDERATIONS

```{r}
summary(Clothing)
```

Since the variable "Card" is categorical, the transformation is performed:

```{r}
Clothing$Card <- as.factor(Clothing$Card)
```


# BOXPLOT NUMERIC VARIABLES

## BOXPLOT RECENCY

```{r, echo=F}
ggplot(Clothing, aes(x=0,y=Recency))+ 
      geom_boxplot(color="black",fill="lightslateblue",alpha=0.2,notch=TRUE,
        notchwidth = 0.8,outlier.colour="red",outlier.fill="red",
        outlier.size=3)+
  stat_summary(fun.y=mean, geom="point", shape=18,size=3, color="red")+
  labs(title="Boxplot Price of Light", y="Price of Light")+
  theme_bw() +
  scale_fill_manual(values=c('lightcyan1'))
```

## BOXPLOT 

```{r, echo=F}
ggplot(Clothing, aes(x=0,y=Recency))+ 
      geom_boxplot(color="black",fill="lightslateblue",alpha=0.2,notch=TRUE,
        notchwidth = 0.8,outlier.colour="red",outlier.fill="red",
        outlier.size=3)+
  stat_summary(fun.y=mean, geom="point", shape=18,size=3, color="red")+
  labs(title="Boxplot Price of Light", y="Price of Light")+
  theme_bw() +
  scale_fill_manual(values=c('lightcyan1'))
```



# REGRESSION MODEL

## SUMMARY OF THE MODEL

We are interested in knowing the relationship of the variable "Amount" with respect to the variable "Dollar24":

```{r include=FALSE}
Clothing=Clothing[-60,]
out <- lm(Amount ~ Dollar24,data=Clothing)
summary(out)
library(knitr)
```

```{r echo=FALSE}
kable(summary(out)$coef, digits=3)
```



**Results:** $y_i=\beta_0+\beta_1x_1+beta_2x_2=-6.2154+ 0.203x_1$

The variable `Dollar24` IS found to be significant for the model.


## PLOT THE MODEL

```{r, echo=F,warning=FALSE}
Clothing=Clothing[-60,]
Clothing$Card <- as.factor(Clothing$Card)
regmodel <- lm(Amount ~ Dollar24, data = Clothing)
plot <- Clothing %>%
  plot_ly(x = ~Dollar24, color = ~Card) %>%
  add_markers(y = ~Amount) %>%
  add_lines(x = ~Dollar24, y = fitted(regmodel))
htmlwidgets::saveWidget(plot,'plotly.html')
knitr::include_url('plotly.html', height = "576px")
```


# THE END