---
title: "**DATA TIDYING PRESENTATION**"
author: "*Amalia Jiménez Toledano*"
output: 
  revealjs::revealjs_presentation:
    theme: sky
    center: T
    self_contained: false
    highlight: kate
    transition: concave
    css: custom.css
    reveal_options:
      slideNumber: true
---


```{r include=FALSE}
library(Stat2Data)
library(ggplot2)
data(Clothing)
summary(Clothing)
library(knitr)
library(plotly)
library(tidyverse)
```

# READ THE DATA AND SUMMARY

**The variables of the data are the following:**

<ul>
<li class="fragment highlight-current-blue" data-fragment-index="1">**ID**: 	Case ID</li>
<li class="fragment highlight-current-red" data-fragment-index="2"> **Amount**: Net dollar amount spent by customers in their latest purchase from this retailer</li>
<li class="fragment highlight-current-green" data-fragment-index="3"> **Recency**:	Number of months since the last purchase</li>
<li class="fragment highlight-current-blue" data-fragment-index="4"> **Freq12**:	Number of purchases in the last 12 months</li>
<li class="fragment highlight-current-red" data-fragment-index="5"> **Dollar12**:	Dollar amount of purchases in the last 12 months</li>
<li class="fragment highlight-current-green" data-fragment-index="6"> **Freq24**:	Number of purchases in the last 24 month</li>
<li class="fragment highlight-current-red" data-fragment-index="7"> **Freq24**:	Number of purchases in the last 24 month</li>
<li class="fragment highlight-current-blue" data-fragment-index="8"> **Dollar24**:	Dollar amount of purchases in the last 24 months</li>
<li class="fragment highlight-current-red" data-fragment-index="9">  **Card**:	1 for customers who have a private-label credit card with the retailer, 0 if not
</li>
</ul>


## DATABASE CONSIDERATIONS

```{r}
summary(Clothing)
```

Since the variable "Card" is categorical, the transformation is performed:

```{r}
Clothing$Card <- as.factor(Clothing$Card)
```


# BOXPLOT NUMERIC VARIABLES

## BOXPLOT RECENCY

```{r, echo=F, warning=FALSE}
ggplot(Clothing, aes(x=0,y=Recency))+ 
      geom_boxplot(color="black",fill="lightslateblue",alpha=0.2,notch=TRUE,
        notchwidth = 0.8,outlier.colour="red",outlier.fill="red",
        outlier.size=3)+
  stat_summary(fun.y=mean, geom="point", shape=18,size=3, color="red")+
  labs(title="Boxplot Recency", y="Recency")+
  theme_bw() +
  scale_fill_manual(values=c('lightcyan1'))
```

## BOXPLOT AMOUNT

```{r, echo=F, warning=FALSE}
Clothing=Clothing[-60,]
ggplot(Clothing, aes(x=0,y=Amount))+ 
      geom_boxplot(color="black",fill="gold3",alpha=0.2,notch=TRUE,
        notchwidth = 0.8,outlier.colour="red",outlier.fill="red",
        outlier.size=3)+
  stat_summary(fun.y=mean, geom="point", shape=18,size=3, color="red")+
  labs(title="Boxplot Amount", y="Amount")+
  theme_bw() +
  scale_fill_manual(values=c('lightcyan1'))
```


# PLOT CATEGORICAL VARIABLE

```{r echo=FALSE}
library(tidyverse)
library(ggplot2)
count.g02=data.frame(
  g02=c("Public-label","Private-label"),
  n=c(40,20),
  prop=c(66.66,33.33)
)
count.g02<- count.g02 %>%
  arrange(desc(g02)) %>%
  mutate(lab.ypos = cumsum(prop) - 0.5*prop)

ggplot(count.g02, aes(x = "", y = prop, fill = g02)) +
  geom_bar(width = 1, stat = "identity", color = "white") +
  coord_polar("y", start = 0)+
  guides(fill=guide_legend(title="Card"))+
  labs(title="Pie Plot Variable Card")+
  geom_text(aes(y = lab.ypos, label = prop), color = "white")+
  scale_fill_manual(values=c("#0073C2FF","#EFC000FF")) +
  theme_void()
```

# REGRESSION MODEL

## SUMMARY OF THE MODEL

We are interested in knowing the relationship of the variable "Amount" with respect to the variable "Dollar24":

```{r include=FALSE}
Clothing=Clothing[-60,]
out <- lm(Amount ~ Dollar24,data=Clothing)
summary(out)
library(knitr)
```

```{r echo=FALSE}
kable(summary(out)$coef, digits=3)
```



**Results:** $y_i=\beta_0+\beta_1x_1+beta_2x_2=-6.2154+ 0.203x_1$

--> The variable `Dollar24` is found to be significant for the model.


## PLOT THE MODEL

```{r, echo=F,warning=FALSE}
Clothing=Clothing[-60,]
Clothing$Card <- as.factor(Clothing$Card)
regmodel <- lm(Amount ~ Dollar24, data = Clothing)
plot <- Clothing %>%
  plot_ly(x = ~Dollar24, color = ~Card) %>%
  add_markers(y = ~Amount) %>%
  add_lines(x = ~Dollar24, y = fitted(regmodel))
htmlwidgets::saveWidget(plot,'plotly.html')
knitr::include_url('plotly.html', height = "576px")
```


# END